Ceph Parallel File System Evaluation Report

### 2013-11-11 introduction.tex
minor fixes for final touch

This rest of the paper is organized as follows. Section~\ref{sec:background}
provides an overview to Ceph and its architectural components;
Section~\ref{sec:testbed} gives an overview on our general test and evaluation
methodology as well as testbed environment; Following it,
Section~\ref{sec:baseline} establishes the baseline performance and
expectations for all critical components on the data path;
Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
bottom up: from middle tier RADOS object layer to the file system-level and
then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
investigative and tuning effort, we compare results before and after, and how
the process eventually bring the system performance to a respectable state.
Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
and future works.

>>>>

This rest of the paper is organized as follows. Section~\ref{sec:background}
provides an overview to Ceph and its architectural components;
Section~\ref{sec:testbed} gives an overview on our general test and evaluation
methodology as well as testbed environment; Following it,
Section~\ref{sec:baseline} establishes the baseline performance and
expectations for all critical components on the data path;
Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
bottom up: from middle tier RADOS object layer to the file system-level
performance. In Section~\ref{sec:ceph-tuning} we highlight the investigative
and tuning effort, we compare results before and after, and how the process
eventually bring the system performance to a respectable state. Finally,
Section~\ref{sec:conclusion} summarizes our findings, observations, and future
works.

### 2013-11-11 testbed.tex
minor fixes for final touch

We used a Data Direct Networks (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. In our testbed, exported RAID groups (LUNs) 
are driven by four server hosts (oss-[1-4]).  Each server host has
two InfiniBand (IB) QDR connections to SFA10K.  We used a single
dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
setup is adequate to drive the SFA10K at its maximum theoretical throughput
(roughly 12 GB/s). 
%Server hosts and SFA10K connection diagram is illustrated in
%Figure~\ref{fig:ddn-sfa10k}.

@@

Our SFA10K system consists of 200 SAS drives and 280 SATA drives.
% hosted in a
%10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
%has two SAS links per controller (four in total). 
The SATA and SAS disks in our
testbed are distributed evenly over the SFA10K.
%ten SA4601 disk trays (20 SAS and 28 SATA
%disks per tray). 
Each SFA10K controller has two RAID processors and each
RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
groups by the RAID processors and then exported to connected
server hosts.
%over the IB connections. 
%Since each SFA10K controller is a
%stand-alone computer system running Linux, CPU and memory affinity while
%organizing disks into RAID groups and exporting them is crucial for obtaining
%top performance out of an SFA10K system.

>>>>

We used a Data Direct Networks (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. In our testbed, exported RAID groups (LUNs)
are driven by four server hosts (oss-[1-4]).  Each server host has two
InfiniBand (IB) QDR connections (supported by a dual-port Mellanox ConnectX IB
card) to SFA10K. By our calculation, this setup is adequate to drive the
SFA10K at its maximum theoretical throughput (roughly 12 GB/s). 
%Server hosts and SFA10K connection diagram is illustrated in
%Figure~\ref{fig:ddn-sfa10k}.

@@

Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
10-tray configuration. 
%Each DDN SA4601 disk tray can host up to 60 disks and has two SAS links per
%controller (four in total). 
The SATA and SAS disks in our testbed are distributed evenly over the SFA10K.
%ten SA4601 disk trays (20 SAS and 28 SATA disks per tray). 
Each SFA10K controller has two RAID processors and each RAID processor hosts a
dual-port IB QDR card. The disks are organized into RAID groups by the RAID
processors and then exported to connected server hosts.
%over the IB connections. Since each SFA10K controller is a stand-alone
%computer system running Linux, CPU and memory affinity while organizing disks
%into RAID groups and exporting them is crucial for obtaining top performance
%out of an SFA10K system.
